Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level, which we call the delta maintainability score. %This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring. 
Based on this score, we extract common factors between clones for a developer to filter their clone output based on the factors and the derived thresholds for them.

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code. This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can. %This subset is based on adapted clone definitions, that are optimized towards automated refactoring. 
Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

\settopmatter{printfolios=true} % TODO: Remove before final version
\maketitle

@@

In this study, we analyze which factors influence the impact of refactoring a clone on maintainability. We create a tool that automatically applies ``Extract Method'' refactorings to a subset of detected clones. We measure several maintainability metrics \cite{heitlager2007practical} before and after refactoring each clone to determine its impact on system maintainability. These metrics are volume, number of parameters, duplication and complexity. Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of projects in a controlled environment. We use this data to understand which characteristics of clones have the biggest influence on system maintainability when refactoring. This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.

@@

We also limited our scope by choosing a set of four metrics. However, software maintainability depends on more factors and can be measured by more metrics. By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring. For instance, we think that module coupling \cite{heitlager2007practical} is an important metric to be considered when refactoring clones. In future work we will investigate other groups of maintainability metrics to broaden the understanding of factors influencing the desirability of a refactoring.

>>>>

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level, which we call the delta maintainability score. Based on this score, we extract common factors between clones for a developer to filter their clone output based on the factors and the derived thresholds for them.

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code. This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can. Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

%\settopmatter{printfolios=true} % TODO: Remove before final version
\maketitle

@@

In this study, we analyze which factors influence the impact of refactoring a clone on maintainability. We create a tool that automatically applies ``Extract Method'' refactorings to a subset of detected clones. We measure several maintainability metrics \cite{heitlager2007practical} before and after refactoring each clone to determine its impact on system maintainability. These metrics are volume, number of parameters, duplication and complexity. Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of projects in a controlled environment. We use this data to understand which characteristics of clones have the biggest influence on system maintainability when refactoring. This allows to suggest more relevant clones for refactoring and can thus assist in the refactoring process.

@@

We also limited our scope by choosing a set of four metrics. However, software maintainability depends on more factors and can be measured by more metrics. By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring. For instance, we think that module coupling \cite{briand1999unified,heitlager2007practical} is an important metric to be considered when refactoring clones. In future work we will investigate other groups of maintainability metrics to broaden the understanding of factors influencing the desirability of a refactoring.
